A Standardized Effect Size for Evaluating the Comparing the Strength of Phylogenetic Signal

### 2020-07-12 Manuscript/Manuscript-8.tex
typos

By contrast, with Blomberg's \(\kappa\), which is positively ubounded,
we might expect that \(\hat{\lambda}\) follows a normal distribution
(\textbf{add ref}). A simulation experiment should reveal that
\(\kappa\) is symmetrically distributed across different strengths of
phylogenetic signal, for any \(\lambda\) used to generate data. This
attribute seemed less reasonable based on the simulations performed by
Münkemüller et al. (20), as distibutions were postively skewed,
suggesting the Blomberg's \(\kappa\) might not behave as a statistic
that follows a noraml distribution. However, because their simulations
used a weighted combination of simulated phylogenetic signal strengths,
strong inferences are not possible (and distributional attributes were
not the intended result of their simulations). For both Pagel's
\(\lambda\) or Blomberg's \(\kappa\), evaluation of statistical moments
across a range of \(\lambda\) used to generate data would be valuable
for adjudicating the relibalilty of these statistics. Furthermore, these
are statistics that appear to have expected values that vary with tree
size (20), making comparisons across studies challenging. Therefore,
transformation of these statistics into \(Z\)-scores in the same
simulation experiments would allow evaluation of the efficacy of each
statistic to yield effect sizes that could be used for comparative
anlyses. \hfill\break

>>>>

By contrast, with Blomberg's \(\kappa\), which is positively ubounded,
we might expect that \(\kappa\) follows a normal distribution
(\textbf{add ref}). A simulation experiment should reveal that
\(\kappa\) is symmetrically distributed across different strengths of
phylogenetic signal, for any \(\lambda\) used to generate data. This
attribute seemed less reasonable based on the simulations performed by
Münkemüller et al. (20), as distibutions were postively skewed,
suggesting the Blomberg's \(\kappa\) might not behave as a statistic
that follows a noraml distribution. However, because their simulations
used a weighted combination of simulated phylogenetic signal strengths,
strong inferences are not possible (and distributional attributes were
not the intended result of their simulations). For both Pagel's
\(\lambda\) or Blomberg's \(\kappa\), evaluation of statistical moments
across a range of \(\lambda\) used to generate data would be valuable
for adjudicating the relibalilty of these statistics. Furthermore, these
are statistics that appear to have expected values that vary with tree
size (20), making comparisons across studies challenging. Therefore,
transformation of these statistics into \(Z\)-scores in the same
simulation experiments would allow evaluation of the efficacy of each
statistic to yield effect sizes that could be used for comparative
anlyses. \hfill\break
